Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-06 paper-1/manuscript.tex
Rev: Concluding paragraph

To sum up, in the full model, STD acted in much the same way as TA, causing both a reduction of the response to the frequently presented standard stimuli (\dev{} B) by local suppression, and an increase in the response to deviant stimuli (\dev{} A) by relief from global suppression, relative to control. Yet, as we showed in Figure \ref{fig7} and in the previous section, a decrease in \dev{} B responses also entailed lower $V_{TA}$, which independently lead to higher \dev{} A responses. Thus, adding STD to the model increased the DDI both directly, through its intrinsic effects in local and global suppression, and indirectly, by altering the pattern of TA by way of local suppression of B.

>>>>

To sum up, in the full model, STD acted in much the same way as TA, causing both a reduction in \dev{} of the response to the frequently presented non-target stimuli by local suppression, and an increase in the response to target stimuli by relief from global suppression, relative to \msc{}. Yet, as we showed in Figure \ref{fig7} and in the previous section, a decrease in \dev{} B responses also entailed lower $V_{TA}$, which independently led to higher \dev{} A responses. Thus, adding STD to the model increased the DDI both directly, through its intrinsic effects in local and global suppression, and indirectly, by altering the pattern of TA by way of local suppression of B.
